
---
title: "Using R and Python Together"
author: "Jaclyn Liu"
date: "2026-09-28"
---

## Introduction

This post demonstrates how R and Python can work together in one Quarto document using the `reticulate` package. I create an object in R, use it in Python, and then pass the Python result back to R.

## Create an object in R

```{r}
library(reticulate)

numbers <- c(10, 20, 30, 40, 50)
numbers
```

The R object `numbers` contains five numeric values.

## Use the R object in Python

```{python}
numbers_from_r = list(r.numbers)

python_mean = sum(numbers_from_r) / len(numbers_from_r)

python_mean
```

Python accesses the object created in R and calculates its mean.

## Use the Python result in R

```{r}
mean_from_python <- py$python_mean
mean_from_python
```

The value calculated in Python is now available in R.

## Verify the result

```{r}
mean(numbers)
```

Both calculations produce the same mean. This demonstrates that an object can be passed from R to Python and that a result computed in Python can then be used in R within the same Quarto document.