---
title: "Untitled"
format: html
---

---
title: "Exploring Fuel Efficiency with R"
author: "Jaclyn Liu"
date: "2026-09-28"
---

## Introduction

In this post, I use R to explore the relationship between vehicle characteristics and fuel efficiency using the `mtcars` dataset.

Data: [`mtcars`](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html), included with R in the `datasets` package.

The dataset contains fuel consumption and automobile design characteristics for 32 cars.

## Inspect the data

```{r}
#| message: false
#| warning: false

head(mtcars)
```

The dataset includes variables such as miles per gallon (`mpg`), vehicle weight (`wt`), horsepower (`hp`), and number of cylinders (`cyl`).

## Summarize fuel efficiency

```{r}
summary(mtcars$mpg)
```

The summary shows considerable variation in fuel efficiency across the 32 vehicles.

## Compare fuel efficiency by cylinder count

```{r}
aggregate(mpg ~ cyl, data = mtcars, FUN = mean)
```

Cars with fewer cylinders have higher average fuel efficiency in this dataset.

## Examine weight and fuel efficiency

```{r}
#| label: fig-weight-mpg
#| fig-cap: "Relationship between vehicle weight and fuel efficiency."

plot(
  mtcars$wt,
  mtcars$mpg,
  xlab = "Weight (1000 lbs)",
  ylab = "Miles per gallon",
  main = "Vehicle Weight and Fuel Efficiency"
)

abline(lm(mpg ~ wt, data = mtcars))
```

The plot shows a negative relationship between vehicle weight and fuel efficiency. Heavier vehicles generally have lower miles per gallon.

## Conclusion

This analysis shows that vehicle characteristics are related to fuel efficiency. In this dataset, heavier cars and cars with more cylinders tend to have lower fuel efficiency.